---
title: "Video Game Sales"
output:
  pdf_document: default
  html_document:
  df_print: paged
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[CO,CE]{Group12-AssignmentR}
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggpubr)
library(tidyverse)
library(janitor) # janitor helps us clean datasets
library(here) # here helps us to know where files are
library(readxl)
library(dplyr)
```

## ______________________________________________
## Introduction
## This dataset contains a list of video games with sales greater than 100,000 copies.
## Fields include:
## Rank - Ranking of overall sales
## Name - The games name
## Platform - Platform of the games release (i.e. PC,PS4, etc.)
## Year - Year of the game's release
## Genre - Genre of the game
## Publisher - Publisher of the game
## NA_Sales - Sales in North America (in millions)
## EU_Sales - Sales in Europe (in millions)
## JP_Sales - Sales in Japan (in millions)
## Other_Sales - Sales in the rest of the world (in millions)
## Global_Sales - Total worldwide sales.


## ______________________________________________
## Load data - vgsales.csv from https://www.kaggle.com/gregorut/videogamesales
```{r VideoGameSales}
VideoGamedata <- readr::read_csv(file ="vgsales.csv")
```

## ______________________________________________
## Structure of dataset
```{r}
str(VideoGamedata)
```

## ______________________________________________
## List the variables in dataset
```{r}
names(VideoGamedata)
```

## ______________________________________________
## Top 15 rows of dataset
```{r}
head (VideoGamedata, 15)
```

## ______________________________________________
## Remove missing values in dataset
```{r chunk-missingvalues,results="hide"}
str(VideoGamedata)
complete.cases(VideoGamedata)
x <- VideoGamedata[complete.cases(VideoGamedata), ]
str(x)
```

## ______________________________________________
## User defined function using any of the variables from the data set
```{r chunk-function,results="hide"}
Total <- function(x,y) 
{x+y}
Total (VideoGamedata$Other_Sales,VideoGamedata$Global_Sales)
```

## ______________________________________________
## Data manipulation techniques and filter rows based on any logical criteria that exist in dataset
```{r}
VideoGamedata %>% filter(Global_Sales > 30.00) 
```

## ______________________________________________
## Dependent & independent variables and use reshaping techniques and create a new data frame by joining those variables from your dataset
```{r}

```

## ______________________________________________
## Remove missing values in dataset
```{r chunk-missingvalue,results="hide"}
##To check missing values in dataset
VideoGameDataNew=is.na(VideoGamedata)
##To remove Missing values from Dataset VideoGameDataNew
na.omit(VideoGameDataNew)
```

## ______________________________________________
## Identify and remove duplicated data in dataset
```{r chunk-duplicate,results="hide"}
VideoGameDataDuplicate =VideoGamedata
##VideoGameDataDuplicate[!duplicated(VideoGameDataDuplicate$Sepal.Width),]
VideoGameDataDuplicate %>% distinct()
```

## ______________________________________________
## Reorder multiple rows in descending order
```{r}

```
## ______________________________________________
## Rename column names in dataset
```{r}

```
## ______________________________________________
## Add new variables in data frame by using a mathematical function
```{r}
VideoGamedata$NAAndEUSales =VideoGamedata$EU_Sales+VideoGamedata$NA_Sales
```
## ______________________________________________
## Create a training set using random number generator engine
```{r cars}
set.seed(1234)
trainingdata = VideoGamedata %>% sample_frac(0.8,replace = FALSE)
```
## ______________________________________________
## Print Summary Statistics of dataset
```{r}
summary(VideoGamedata)
```
## ______________________________________________
## Use numerical variables from the dataset and perform the statistical functions - mean
```{r}
VideoGamedata %>%
  summarise(
    count = n(),
    mean_NorthAmericaSales = mean(VideoGamedata$NA_Sales, na.rm = TRUE),
    mean_EuropeSales = mean(VideoGamedata$EU_Sales, na.rm = TRUE),
    mean_JapanSales = mean(VideoGamedata$JP_Sales, na.rm = TRUE),
    mean_OtherSales = mean(VideoGamedata$Other_Sales, na.rm = TRUE),
    mean_GlobalSales = mean(VideoGamedata$Global_Sales, na.rm = TRUE)
  )
```
## ______________________________________________
## Use numerical variables from the dataset and perform the statistical functions - median
```{r}
VideoGamedata %>%
  summarise(
    count = n(),
    median_NorthAmericaSales = median(VideoGamedata$NA_Sales, na.rm = TRUE),
    median_EuropeSales = median(VideoGamedata$EU_Sales, na.rm = TRUE),
    median_JapanSales = median(VideoGamedata$JP_Sales, na.rm = TRUE),
    median_OtherSales = median(VideoGamedata$Other_Sales, na.rm = TRUE),
    median_GlobalSales = median(VideoGamedata$Global_Sales, na.rm = TRUE)
  )
```
## ______________________________________________
## Use numerical variables from the dataset and perform the statistical functions - range
```{r}
VideoGamedata %>%
  summarise(
    count = n(),
    mode_NorthAmericaSales = range(VideoGamedata$NA_Sales, na.rm = TRUE),
    mode_EuropeSales = range(VideoGamedata$EU_Sales, na.rm = TRUE),
    mode_JapanSales = range(VideoGamedata$JP_Sales, na.rm = TRUE),
    mode_OtherSales = range(VideoGamedata$Other_Sales, na.rm = TRUE),
    mode_GlobalSales = range(VideoGamedata$Global_Sales, na.rm = TRUE)
  )
```
## ______________________________________________
## Find the correlation between any 2 variables by applying least square linear regression model - correlation
```{r}
X = VideoGamedata[,"Global_Sales"]
Y = VideoGamedata[,"JP_Sales"]
CORRELATION = cor(Y,X,method = "pearson")
CORRELATION
```

## ______________________________________________
## Plot a scatter plot for any 2 variables in your dataset - graph in correlation
```{r}
ggscatter(VideoGamedata, x = "Global_Sales", y = "JP_Sales",add = "reg.line", conf.int = TRUE,cor.coef = TRUE, cor.method = "pearson",xlab = "Global_Sales", ylab = "JP_Sales")
```

## ______________________________________________
## graph - bar plot Global_Sales
```{r test}
ggplot(data = VideoGamedata,aes(x = Genre)) + geom_bar()
```

## ______________________________________________
## Plot a bar plot for any 2 variables in your dataset - barplot Global_Sale with Genre
```{r}
ggplot(data = VideoGamedata,aes(x = VideoGamedata$Global_Sales,fill = factor(VideoGamedata$Genre))) + geom_bar()+ xlim(0, 20) + ylim(0, 50)
```

## ______________________________________________
## Scatter plot
```{r}
ggplot(data = VideoGamedata,aes(x = Global_Sales,y = JP_Sales,col = factor(Genre)))+ geom_point()
```

## ______________________________________________
## Conclusion of your analysis